---
title: "Codebook"
author: "Nikki Rayner"
date: "12/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting and Cleaning Data Codebook

Variables:

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAccXYZ and tGyroXYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerkXYZ and tBodyGyroJerkXYZ). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag). 

Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAccXYZ, fBodyAccJerkXYZ, fBodyGyroXYZ, fBodyAccJerkMag, fBodyGyroMag, fBodyGyroJerkMag. (Note the 'f' to indicate frequency domain signals). 

These signals were used to estimate variables of the feature vector for each pattern:  
'XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

```{r echo=FALSE, results='asis'}
library(knitr)
variables1 <- read.csv("./Data/Assignment_3.4_Data/Variables.csv", header = TRUE)
kable(variables1, caption = "Variable types")
```


Two variables are available for each of the above - the mean (mean) or standard deviation (std). 

See full list of variables below:

```{r echo=FALSE, results='asis'}
library(knitr)
kable(variables2, caption = "Variables")
```
